% !TEX program = xelatex
% xelatex
\documentclass[]{friggeri-cv}

\begin{document}

\header{Miguel Angel}{López Hernández}{Free and Open Source Software/Hardware enthusiast, advocate and developer}

%------------------------------------------------------------------------------
% SIDEBAR SECTION
%------------------------------------------------------------------------------
\begin{aside} % In the aside, each new line forces a line break
    \section{About}
    Experienced, proactive, problem solver, team player, but above all, continuous and passionate learner of emerging technologies\ldots and life.
    ~
    \section{Contact}
    {\faMapMarker} México
    ~
    \website{gulev.org}~{\nfURL}
    \email{miguel@gulev.org}~{\nfURL}
    \youtube{GulevOrg}~{\nfURL}
    \facebook{GulevOrg}~{\nfURL}
    \twitter{MiguelALH}~{\nfURL}
    \telegram{MiguelALH}~{\nfURL}
    \instagram{MiguelALH}~{\nfURL}
    \linkedin{MiguelALH}~{\nfURL}
    \github{MiguelALH}~{\nfURL}
    \phone{Please ask}~{\nfURL}
    ~
    \section{Languages}
    Spanish (native)
    English
    ~
    \section{Programming}
    {\color{black} $\varheartsuit$} Python, PHP, C, Perl, Java, Node (JavaScript/TypeScript), R, C\#, Dart, Go, Rust, Shell Scripting, HTML, CSS, {\LaTeX}
    ~
    \section{Interests}
    I’m currently very interested and involved in \textbf{Machine Learning and Data Science} and its application in various fields.
\end{aside}

\begin{center}
    \large{\textbf{\textit{"Maybe I don't know it yet, but you can be sure, I'll learn it."}}}
\end{center}

\section{Experience}

\begin{entrylist}
    \entry%
    {Since 2019}
    {Senior Free \& Open Source Software Architect}
    {Softtek - Digital Architecture}
    {Design of IT Architectures for optimization of resources and migration to the Cloud in the financial, health, automotive, courier/parcel and logistics sectors, among others.}
\end{entrylist}

\begin{entrylist}
    \entry%
    {Since 1997}
    {Managing Director}
    {GULEV Free \& Open Source Software/Hardware AC}
    {I organized \textbf{the first ever Free Software conference in Mexico}, the \href{http://gulev.org.mx/eventos/gulev2001}{GULEV Congreso GNU/Linux 2001~{\nfURL}} and \href{http://gulev.org.mx/conferences}{all those that followed~{\nfURL}}. Member of the \textbf{GNOME Foundation} and the \href{https://www.gnome.org/}{\textbf{GNOME Project}~{\nfURL}} for many years and a \textbf{pioneer in the use and development of Free and Open Source Software in Mexico}. }
\end{entrylist}

\begin{entrylist}
    \entry%
    {Since 1992}
    {Software Developer/CTO}
    {LG Internet Solutions}
    {I have been developing projects for more than 28 years, \textbf{\textit{particularly with Free \& Open Source Software for the last 26 years}}. I created \textbf{a Linux distribution} (\href{https://distrowatch.com/table.php?distribution=lgis}{LGIS GNU/Linux~{\nfURL}}), which included the latest security updates released by RedHat and the \href{https://en.wikipedia.org/wiki/Ximian}{Ximian Desktop~{\nfURL}}, with the support of \href{https://www.linkedin.com/in/natfriedman/}{Nat Friedman~{\nfURL}}, now CEO at GitHub. \textbf{Free \& Open Source Hardware} solutions.}
\end{entrylist}

\section{Technical skills}

\begin{multicols}{2}
    \subsection{Cloud/DevOps}
    AWS, Azure, GCP, Docker, Kubernetes, Terraform, Rancher, Proxmox, Ansible, Jenkins, Git, Fluentd, Prometheus, Grafana.
 
    \subsection{Operating Systems}
    {\faLinux}~Linux (Debian/RedHat/ArchLinux \& derivatives), {\nfBsd}~~BSD (FreeBSD, OpenBSD), {\faApple}~macOS, {\nfWindows}~~windows.

    \subsection{DBMS}
    PostgreSQL, MySQL/MariaDB, SQL Server, Sybase, Oracle, NoSQL (MongoDB/CouchDB/CouchBase).
    
    \subsection{Mobile Development (Native/Hybrid)}
    Kotlin, Flutter, React Native, Java, Swift, Ionic, PhoneGap, Apache Cordova.

    \subsection{API Dev/A\&A}
    REST, GraphQL, JWT, Oauth, Keycloak, WSO2.

    \subsection{Various}
    Django, Flask, Sencha Ext JS, Angular, Vue.js, PHP Frameworks, Drupal, Odoo, TensoFlow, Pandas, OpenCV, Asterisk \& Derivatives.

\end{multicols}

\section{Education}

\begin{entrylist}
    \entryedu%
    {2018-Present}
    {Bachelor's of Applied Technology}
    {BYU Idaho - BYU Pathway Worldwide}
\end{entrylist}

\begin{entrylist}
    \entryedu%
    {1990-1994}
    {Bachelor's of Computer Science}
    {Universidad Veracruzana}
\end{entrylist}

\end{document}